---
title: "Analysis Report"
format: 
  html: default
  pdf: 
    toc: false
page-navigation: true
---



```{r}
library(ggplot2)
# Read discharged_patients.txt into a dataframe

df <- read.table("discharged_patients.txt", header = TRUE, sep = ",", stringsAsFactors = FALSE)

total_rows <- nrow(df)
total_icu_admit <- sum(tolower(df$icuAdmit) == 'true')
total_ward_admit <- total_rows - total_icu_admit
df$los <- df$dischargeTime - df$admitTime

```

## Total Patients: `{r} total_rows`
### ICU admit %: `{r} total_icu_admit/total_rows`
 

## Icu-vs-Ward-Admits

```{r}
# Pie chart of ICU vs Ward admits

admit_counts <- data.frame(
  type = c("ICU", "Ward"),
  count = c(total_icu_admit, total_ward_admit)
)
ggplot(admit_counts, aes(x = "", y = count, fill = type)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  labs(title = "ICU vs Ward Admits", x = NULL, y = NULL, fill = "Admit Type") +
  theme_void()
```



---

## LOS

```{r}
icu_patients <- df[tolower(df$icuAdmit) == "true", ]
ward_patients <- df[tolower(df$icuAdmit) == "false", ]
q3 <- quantile(df$los, 0.75, na.rm = TRUE)
ggplot(df, aes(x = los, color = icuAdmit)) +
  geom_histogram(binwidth = 0.1) +
  xlim(NA, q3)

summary(icu_patients$los)
summary(ward_patients$los)


total_ward_discharge <- sum(tolower(df$dischargeLocation) == 'ward')
total_icu_discharge <- sum(tolower(df$dischargeLocation) == 'icu')
total_transfers_ward <- sum(df$transferTime != -1 & tolower(df$admitLocation) == 'icu')
total_transfers_icu <- sum(df$transferTime != -1 & tolower(df$admitLocation) == 'ward')

```
## Summary Stats

 key   | value   
-----|-----
Total Admissions | `{r} total_rows`
Total to Ward| `{r} total_ward_admit`
Total to ICU| `{r} total_icu_admit`
% icu/total|     `{r} total_icu_admit/total_rows`
total discharges from ward| `{r} total_ward_discharge`
total dicharges from icu| `{r} total_icu_discharge`
total transfers to ward| `{r} total_transfers_ward`
total transfers to icu| `{r} total_transfers_icu`
fraction of admissions with transfer to WARD| `{r} total_transfers_ward/total_rows`
fraction of admissions with transfer to ICU| `{r} total_transfers_icu/total_rows`
Average LOS| `{r} mean(df$los)` 
average LOS for ICU-admits| `{r} mean(icu_patients$los)` 
average length of stay on ICU (transfer or otherwise)| tbd 
 

---



<!-- Content for transfer vs not page -->

# HCW Visits
## Summary Stats:
key | val 
-----|-----
Average total visits per hcw/shift | val
average daily visits per patient per hcw per shift | val
average distinct patients visited per shift per hcw type | val
average time between visits per HCW by type | val
average number of HCW visits per day/patient (total/{type}) |val
average time between visist by HCW per patient | val
average distinct hcw visits per day by patient | val

